#Caricamento package

```{r packages, message=FALSE}
library(devtools)
require(riv)
library(woe)
require(ggplot2)
require(dplyr)
require(GGally)
require(tidyr)
require(caret)
require(DAAG)
library(pROC)
library(ROCR)
require(MASS)
```

#Set up cartelle e creazione dataset

```{r directory e dataset}
getwd()
setwd("/Users/Americo/Documents/Education/Unitelma/tesi/data_analysis/dataset")
bank0_df <- read.csv(file = "bank_full.csv", sep = ";")
bank0 <- tbl_df(read.csv(file = "bank_full.csv", sep = ";"))
bank0_sm <- read.csv(file = "bank.csv", sep = ";")
```

#Informazioni sul dataset

##Input variables

###bank client data
 
* 1 - age (numeric)
*    2 - job : type of job (categorical: "admin.","unknown","unemployed","management","housemaid","entrepreneur","student", "blue-collar","self-employed","retired","technician","services") 
*    3 - marital : marital status (categorical: "married","divorced","single"; note: "divorced" means divorced or widowed)
*    4 - education (categorical: "unknown","secondary","primary","tertiary")
*    5 - default: has credit in default? (binary: "yes","no")
*    6 - balance: average yearly balance, in euros (numeric) 
*    7 - housing: has housing loan? (binary: "yes","no")
*    8 - loan: has personal loan? (binary: "yes","no")
*    # related with the last contact of the current campaign:
*    9 - contact: contact communication type (categorical: "unknown","telephone","cellular") 
*   10 - day: last contact day of the month (numeric)
*   11 - month: last contact month of year (categorical: "jan", "feb", "mar", ..., "nov", "dec")
*   12 - duration: last contact duration, in seconds (numeric)

###Other attributes:

*   13 - campaign: number of contacts performed during this campaign and for this client (numeric, includes last contact)
*   14 - pdays: number of days that passed by after the client was last contacted from a previous campaign (numeric, -1 means client was not previously contacted)
*   15 - previous: number of contacts performed before this campaign and for this client (numeric)
*   16 - poutcome: outcome of the previous marketing campaign (categorical: "unknown","other","failure","success")

##Output variable (desired target)

*   17 - y - has the client subscribed a term deposit? (binary: "yes","no")

It should be stressed that due to internal competition and current financial crisis, there are huge pressures for European banks to increase a financial asset. To solve this issue, one adopted strategy is offer attractive long-term deposit applications with good interest rates, in particular by using directed marketing campaigns. Also, the same drivers are pressing for a reduction in costs and time. Thus, there is a need for an improvement in efficiency: lesser contacts should be done, but an approximately number of successes (clients subscribing the deposit) should be kept.

##Missing Attribute Values
None

#Esplorazione del dataset

##Esplorazione dimensioni

```{r exp dataset}
str(bank0)
dim(bank0)
```

Non ci sono variabili numeriche, solo interi e fattori. Da capire se servirà qualche trasformazione